\section[Version Control]{What is version control and why do we need it?}

\begin{frame}[c]%
  \begin{center}%
    \Huge\color{vertexDarkRed}What is version control and why do we need it?%
  \end{center}%
\end{frame}%


\begin{frame}[c]{What is Version Control?}
  \begin{itemize}
    \item Version Control tracks changes of a (collection of) document(s)
    \item This can basically be anything:
      \begin{itemize}
        \item software
        \item legal documents
        \item documentation
        \item scientific paper
        \item images
        \item ...
      \end{itemize}
    \item We will call a snapshot of such a collection a \enquote{revision}.
    \item Revisions are the complete history of our projects
  \end{itemize}
\end{frame}

\begin{frame}[c]{Why Use Version Control?}
  \begin{itemize}
    \item Allows us to go back to arbitrary revisions
    \item Shows differences between revisions
    \item Enables collaborative working
    \item Acts as backup
  \end{itemize}
\end{frame}

\begin{frame}[c]{Why Use Version Control?}
  Most Version Control Systems (VCS) make answering the following questions easy:
  \begin{description}
    \item[What?] What changed from revision \emph{A} to revision \emph{B}?
    \item[Who?] Who made a change? Who contributed?
    \item[Why?] VCS usually encourage or even force adding explanations to changes.
    \item[When?] In which revision was a bug introduced or fixed?
  \end{description}

  \onslide<2>{%
    \begin{center}
      \Large\textcolor{vertexDarkRed}{Version Control is a basic requirement for reproducible science}  
    \end{center}
  }
\end{frame}
